### 2018-01-23 project.tex
updated prop 1 and 2
prop 2 is likely garbage. Stared at it for hours and got no where.

  \begin{definition}
    A topology is...
  \end{definition}

  \begin{theorem}
    An arbitrary intersetion of closed sets is closed.
  \end{theorem}

  \begin{proof}
    Because.
  \end{proof}

\end{document}

>>>>

  \begin{proposition}
      Any finite union of closed sets is closed, and any arbitrary intersection of closed sets is closed.
  \end{proposition}

  \begin{proof}
  	Proposition 1 - Any finite union of closed sets is closed.
  	\newline
  	Let C, D be closed sets.
  	\newline
  	Let A, B be compliments of C, D so A, B are open.
  	\newline
  	Then, A $\cap$ B is also open.
  	\newline
  	Thus, X$\setminus$(A $\cap$ B) is closed.
  	\newline
  	X$\setminus$(A $\cap$ B) = X$\setminus$A $\cap$ X$\setminus$B = C $\cup$ D
  	\newline\newline
  	Inductive Proof:
  	\newline
  	$\mathcal{C}_1$ = C $\cup$ D, $\mathcal{C}_1$ is closed.
  	\newline
  	$\mathcal{C}_2$ = $\mathcal{C}_1 \cup$ E, $\mathcal{C}_2$ is closed.
  	\newline
  	$\mathcal{C}_n$ = $\mathcal{C}_1 \cup \mathcal{C}_2 \cup ... \cup \mathcal{C}_(n-1)$, $\mathcal{C}_n$ is closed.
  	\newline
  	$\mathcal{C}_(n+1)$ = $\mathcal{C}_n \cup$ Z, $\mathcal{C}_(n+1)$ is closed.
  	\newline\newline
  	Proposition 1 - Any arbitrary intersection of closed sets is closed.
  	\newline
  	Let $\mathcal{C}$ be a collection of closed sets.
  	\newline
  	Let $\mathcal{U}$ be the compliment of $\mathcal{C}$, so $\mathcal{U}$ is a collection of open sets.
  	\newline
  	Then, $\bigcup \mathcal{U}$ is also open.
  	\newline
  	Thus, X$\setminus\bigcup\mathcal{U}$ is closed.
  	\newline
  	X$\setminus\bigcup\mathcal{U}$ = $\bigcap\mathcal{C}$
  	\newline
  	Therefore, $\bigcap\mathcal{C}$ is closed.
	\end{proof}

	\begin{proposition}
		A set K in a topological space X is closed if and only if K contains all its limit points.
	\end{proposition}
	\begin{proof}
	Proposition 2
	\newline
	Let K = X, then K is closed because $\emptyset$ is open.
	\newline
	Let x $\in$ X$\setminus$K, so x is not a limit point of K.
	\newline
	$\exists \ell \in \mathcal{U}_\ell \in \tau$ such that $\forall$ k $\in$ K besides $\ell$, k $\not\in \mathcal{U}_\ell$
	\newline
	Therefore, $\mathcal{U}_\ell$ is the compliment of K, so $\mathcal{U}_\ell$ is open.
	\newline
	$\mathcal{U}_\ell$ = X$\setminus$K
	\newline
	Thus, X$\setminus$K = $\bigcup$ { $\ell \in \mathcal{U}_\ell$ : $\ell \neq$ k } is open. 
	\end{proof}
\end{document}
